\documentclass[10pt]{beamer} %
\usetheme{Boadilla}
\usecolortheme{beaver}
\usepackage[spanish]{babel}
\usepackage[utf8x]{inputenc}
\usefonttheme{professionalfonts}
\usepackage{times}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{tabulary}
\usepackage{pgfgantt}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}
\usepackage{adjustbox}
\usepackage{soul}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{amsthm}

\newtheorem{Teo}{Teorema}
\newtheorem{prop}{{\it Proposition}}[section]
\setbeamertemplate{itemize item}{\color{red}$\blacksquare$}
\usepackage{hyperref}
\title{avance1}

\title{Hierarchical Bayesian Model for Insurance Claims}
%\institute[Yachay Tech]{School of Mathematical and Computational Sciences, Yachay Tech University, Ecuador}
\author[]{Erika Rivadeneira\\ School of Mathematical and Computational Sciences, Yachay Tech University, Ecuador
\vspace{0.25cm}
\\{\small{\textbf{Tutor:} }}}




\date{\today}

\begin{document}
\tikzstyle{every picture}+=[remember picture]
\lstset{}   
\everymath{\displaystyle}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}
\frametitle{Summary}
\tableofcontents
\end{frame}

%------------------------------------------------------
\section{Introduction}
%------------------------------------------------------

\begin{frame}
\frametitle[9pt]{Introduction}
\begin{itemize}
    \item 
    
\end{itemize}

\end{frame}
%------------------------------------------------------------------------------------


%---------------------------------------------------------------------------------------------
\section{Theoretical Aspects of the Project}
%-------------------------------------------------------------------------------------------
\begin{frame}
\frametitle[9pt]{Theoretical Aspects of the Project}

\begin{itemize}
    \item 
\end{itemize}
\end{frame}
%--------------------------------------------------------------

%--------------------------------------------------------------
\section{References}
%--------------------------------------------------------------
\begin{frame}{References}
    \begin{itemize}
    \item Dimakos, X. and Frigessi, A. (2002). Bayesian premium rating with latent structure. Scan-
dinavian Actuarial Journal, 2002(3):162--184. 
        \item Gamerman, D. (1997). Markov Chain Monte Carlo: Stochastic Simulation for Bayesian
Inference. CRC Press.
\item Migon, H. and Gamerman, D. (1993). Generalized exponential growth models-a Bayesian approach. Journal of Forecasting, 12(7):573--584.
\item Migon, H. and Moura, F. (2005). Hierarchical Bayesian collective risk model: an application to health insurance. Insurance: Mathematics and Economics, 36(2):119--135.
\item Migon, H. and Penna, E. (2006). Bayesian analysis of a health insurance model. Journal of Actuarial Practice, 13:61--80.
\item Pettitt, A. N., Weir, I. S., and Hart, A. G. (2002). A conditional autoregressive gaussian
process for irregularly spaced multivariate data with application to modelling large
sets of binary data. Statistics and Computing, 12(4):353--367.
\item Souza, D., Moura, F., and Migon, H. (2009). Small area population prediction via hierar-
chical models. In Survey Methodology, volume 39 of Catalogue No. 12-001-X, pages
203--214. Statistics Canada.
    \end{itemize}
\end{frame}

\end{document}
